Analysis paper

### 2021-05-04 analysis/analysis.Rmd
update plots

>>>>

```{r, eval = TRUE}
scores_full <- eval_forecasts(
  data[, horizon := substring(target, 1, 1)], 
  summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
  compute_relative_skill = FALSE, 
  baseline = "Baseline"
)

means <- scores_full[, .(meanval = mean(interval_score), 
                         medianval = median(interval_score)), 
                     by =c("model", "location_target", "horizon")]

scores_full %>%
  ggplot(aes(y = interval_score, x = horizon, 
             fill = model, color = model)) +
  geom_boxplot(outlier.shape = 21, coef = 1.5, 
               width=0.5, alpha = 1, 
               position = position_dodge2(width = 0.5)) + 
  # geom_line(data = means, 
  #           aes(group = model, y = meanval, color = model), 
  #           position = position_dodge2(width = 0.5), 
  #           size = 2) +
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_color_brewer(palette = "Accent") + 
  geom_point(data = means, 
             mapping = aes(y = meanval, fill = model),
             color = "black",
             # fill = "red",
             shape = 21,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
    geom_point(data = means, 
             mapping = aes(y = medianval, fill = model),
             color = "black",
             # fill = "red",
             shape = 22,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
  scale_fill_brewer(palette = "Accent") + 
  scale_y_log10() + 
  facet_wrap( ~ location_target, scales = "free") + 
  theme(legend.position = "bottom")

ggsave("plots/scores_horizons.png")
